HPC On-boarding

### 2016-01-20 hpc_101/paper.tex
completiong of partition detail table

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------
%\documentclass[t]{beamer}
\documentclass[t,hyperref={pdfpagelabels=false}]{beamer}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{etoolbox}
\usepackage{lmodern}% http://ctan.org/pkg/lm
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{anyfontsize}
\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{calc}

\mode<presentation> {

@@

@@

\begin{frame}[fragile]
\frametitle{Partition Details}\tiny
\begin{tabular}{c c c c c c c}
  \toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt\\Mode} & \textbf{Mem per CPU} \\
\midrule 
community.q & \begin{tabular}{c c}\textbf{Def}&\textbf{Max}\\00:10:00&3-00:00:00\end{tabular} & \begin{tabular}{c c}\textbf{Min}&\textbf{Max}\\1&20\end{tabular} & 10 & NO & OFF &  \begin{tabular}{c c}\textbf{Def}&\textbf{Max}\\3250&6500\end{tabular}\\
exclusive.q & \begin{tabular}{c  c}\textbf{Def}&\textbf{Max}\\00:10:00&3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min}&\textbf{Max}\\1&20\end{tabular} & 10 & NO & OFF &  \begin{tabular}{c  c}\textbf{Def}&\textbf{Max}\\3250&6500\end{tabular}\\
\bottomrule 
\end{tabular}

%% \begin{columns}[t]
%%   \begin{column}{.3\textwidth}\begin{semiverbatim}\tiny
%% PartitionName=community.q
%%    DefaultTime=00:10:00
%%    MaxTime=3-00:00:00 
%%    MinNodes=1
%%    MaxNodes=20 
%%    Nodes=prod2-[0003-0085]
%%    Priority=10
%%    Shared=NO 
%%    PreemptMode=OFF
%%    DefMemPerCPU=3250 
%%    MaxMemPerCPU=6500
%% \end{semiverbatim}
%%   \end{column}

%% \begin{column}{.3\textwidth}\begin{semiverbatim}\tiny
%% PartitionName=exclusive.q
%%    DefaultTime=00:10:00 
%%    MaxTime=3-00:00:00 
%%    MinNodes=1 
%%    MaxNodes=20 
%%    Nodes=prod2-[0003-0085]
%%    Priority=10
%%    Shared=EXCLUSIVE 
%%    PreemptMode=OFF
%%    DefMemPerNode=UNLIMITED 
%%    MaxMemPerCPU=6500
%% \end{semiverbatim}
%% \end{column}

%% \begin{column}{.3\textwidth}\begin{semiverbatim}\tiny
%% PartitionName=lm.q
%%    DefaultTime=00:10:00
%%    MaxTime=3-00:00:00 
%%    MinNodes=1 
%%    MaxNodes=1 
%%    Nodes=lm2-[0001-0006]
%%    Priority=10
%%    Shared=NO
%%    PreemptMode=REQUEUE
%%    DefMemPerNode=UNLIMITED 
%%    MaxMemPerCPU=262100
%% \end{semiverbatim}
%% \end{column} 
%% \end{columns}

%% \begin{columns}[t]
%% \begin{column}{.3\textwidth}\begin{semiverbatim}\tiny
%% PartitionName=kill.q
%%    DefaultTime=00:10:00
%%    MaxTime=3-00:00:00
%%    MinNodes=1
%%    MaxNodes=12
%%    Nodes=prod2-[0085-0176]
%%    Priority=10
%%    Shared=NO
%%    PreemptMode=REQUEUE
%%    DefMemPerCPU=3250
%%    MaxMemPerCPU=6500

%% \end{semiverbatim}
%% \end{column}

%% \begin{column}{.3\textwidth}\begin{semiverbatim}\tiny
%% PartitionName=htc.q
%%    DefaultTime=00:10:00
%%    MaxTime=3-00:00:00 
%%    MinNodes=1 
%%    MaxNodes=1 
%%    Nodes=prod2-[0001-0176]
%%    Priority=1
%%    Shared=NO
%%    PreemptMode=REQUEUE
%%    DefMemPerCPU=3250 
%%    MaxMemPerCPU=6500
%% \end{semiverbatim}
%% \end{column}

%% \begin{column}{.3\textwidth}\begin{semiverbatim}\tiny
%% PartitionName=sb.q
%%    DefaultTime=00:05:00
%%    MaxTime=01:00:00
%%    MinNodes=1
%%    MaxNodes=2
%%    Nodes=prod2-[0177-0178]
%%    Priority=10 
%%    Shared=NO 
%%    PreemptMode=REQUEUE
%%    DefMemPerCPU=3250 
%%    MaxMemPerCPU=6500
%% \end{semiverbatim}
%% \end{column} 
%% \end{columns}

More details on partition constraints can be viewed by visiting the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command
\begin{itemize}\footnotesize
\item[] \texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\item[] Example: \texttt{$[$login \ctilde$]$\$ scontrol show partition community.q}
\end{itemize}

>>>>

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

%https://tex.stackexchange.com/questions/74353/what-commands-are-there-for-horizontal-spacing
%https://tex.stackexchange.com/questions/80212/controling-padding-using-the-xstring-package
%https://tex.stackexchange.com/questions/2441/how-to-add-a-forced-line-break-inside-a-table-cell
%https://en.wikibooks.org/wiki/LaTeX/Tables#The_tabularx_package
%https://tex.stackexchange.com/questions/312/correctly-typesetting-a-tilde
%https://tex.stackexchange.com/questions/34580/escape-character-in-latex
%https://tex.stackexchange.com/questions/54180/how-do-i-write-something-at-the-end-of-the-slide-in-beamer
%http://code.hammerpig.com/add-footnote-number-latex.html
%https://tex.stackexchange.com/questions/51452/reduce-spacing-in-table-of-contents-beamer
%https://www.sharelatex.com/learn/Using_colours_in_LaTeX
%http://www.math-linux.com/latex-26/article/how-to-make-a-presentation-with-latex-introduction-to-beamer
%https://stackoverflow.com/questions/3594329/semi-transparent-text-in-beamer-pdflatex
%https://www.sharelatex.com/blog/2013/08/16/beamer-series-pt3.html

%\documentclass[t]{beamer}
\documentclass[t,hyperref={pdfpagelabels=false}]{beamer}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{etoolbox}
\usepackage{lmodern}% http://ctan.org/pkg/lm
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{anyfontsize}
\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{calc}
\usepackage{makecell}
\usepackage{xstring}
\mode<presentation> {

@@

\newcommand\padfrom[2]{\StrLen{#2}[\templen]\StrGobbleLeft{#1}{\templen}#2}

@@

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
\toprule                                                                    
\toprule                                                                    
%\midrule
%\midrule
community.q & \begin{tabular}{l r} \textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min}& \padfrom{\ \ \ }{1}~\\ \textbf{Max}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
kill.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{12}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
htc.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
lm.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ }{262100}\end{tabular}\\
\hline
sb.q & \begin{tabular}{l r}\textbf{Default} & 0-00:05:00~\\ \textbf{Max} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}
